A number of research areas such as voice and face recognition are based on designing automated methods to recognize and distinguish individuals based on certain data cues (e.g. audio or visual)~\cite{tolba2006face}. Along similar lines, this work investigates whether or not individuals (specifically artists) are distinguishable by the way they sketch and if so, the extent to which this uniqueness can be used to identify their sketches or to detect sketch fraud. To the best of our knowledge, this work is the first to focus on authorship recognition from 2D sketch images. In this paper, we propose a new method called sketch authorship recognition, denoted as SAR. The SAR approach assumes that the uniqueness of an artist's sketch style can be determined by the frequency in which he/she uses certain basic strokes, even though these strokes are universal to all artists. It is reasonable to assume that the unique style of an artist manifests itself in the artist's choice of particular stroke over others, as well as, the artist's frequency in using each type of stroke. For example, Disney characters tend to have more rounded strokes using nearly elliptic curves. However, other cartoon companies such as Looney Tunes prefer to adorn their characters with straighter and sharper strokes. Therefore, by extracting strokes from a digitized sketch, this sketch can be represented as a histogram of universal strokes. In turn, this representation is used to compare the inherent style of the sketch to a database of sketches whose authorship is already known. As illustrated in Figure ~\ref{pipeline}, our proposed SAR approach consists of five major steps: obtaining sketches drawn by different artists, extracting strokes from each sketch, splitting strokes into segments that expose authorship, examining the characteristics of these segments to represent each sketch using features derived from these characteristics, and classifying authorship using this representation.

%\B{This is an old reference. We will need to update it.}

%SAR is based on first extracting a number of local features that are used to build a visual vocabulary of strokes. Then, a new representation of the sketches is built using the obtained strokes vocabulary so that it conveys information related to a particular artist's style.
\vspace{-1mm}
SAR is expected to be useful in a variety of applications such as fraud detection (i.e. fraudulent versus original sketches), where there is a need to examine fine-grained stroke-level features to discriminate sketches that \emph{look} very similar. This problem cannot be approached using existing shape matching techniques, which are unable to detect local and fine differences. Also, these methods are heavily dependent on the content of the sketch and not its stlye. They would merely place sketches representing the same object but drawn by different artists with different styles under the same category. Moreover, SAR can play a major role in artistic style training and reproduction, since it can be used to quantitatively assess how the sketching style of an artist in-training is becoming similar to a desired target style throughout the training process. For example, newly recruited artists at Disney
are required to undergo a six month training procedure to familiarize themselves with the company's sketch techniques. This is done to ensure that new and already existing characters can be created with the same Disney \emph{look}. Clearly, there is an immediate need for an automated technique to examine and monitor how an artist progresses during his/her sketch style training. Other areas that can make use of SAR include handwriting verification, design patent litigation and brand marking.

%Techniques used in SAR can also be extended to handwriting verification applications, since automatic techniques that analyze handwriting authorship using detailed low-level features do not exist \B{I dont know whether we should say this. Reviewers might expect to see results}.
\vspace{-1mm}
\textbf{Contributions:} In this work, \textbf{(1)} we propose a novel method of sketch authorship recognition (SAR) based on the hypothesis that the collection of an artist's strokes in a sketch are unique to that artist and they can be used to define his/her style. The uniqueness in stroke usage can also be used to detect sketch fraud. \textbf{(2)} We compile 2 different sketch datasets collected from  a number of experienced artists. These datasets are designed to expose SAR to different levels of challenges and sketch variations so as to test its effectiveness in authorship recognition. They will be made publicly available, along with SAR source code, to allow for further research on this topic. \textbf{(3)} We develop two SAR-enabled sketch applications. The first provides artists in-training with immediate feedback on how close their sketching style is to a particular target style and monitors their progress throughout the training period. The other provides the first quantitative and automatic measure to evaluate the quality of automatic sketch synthesis tools.

%The paper is organized as follows. First, we survey the literature most related to SAR. Next, Section \ref{sec:SAR} presents a detailed description of SAR and its underlying modules. In Section \ref{sec:humanexps}, we present the details of the different datasets compiled in this work as well as 2 extensive user studies that validate the difficulty of the stroke authorship problem. Extensive experimental results and two sample applications of SAR are presented in Sections \ref{sec:exp} and \ref{sec:app} respectively. We conclude the paper and highlight future work in Section \ref{sec:conclusions}.


%As illustrated in Figure ~\ref{pipeline}, the proposed SAR approach consists of five major steps: obtaining sketches drawn by different artists, extracting strokes from each sketch, splitting strokes into segments that expose authorship, examining the characteristics of these segments to represent each sketch using features derived from these characteristics, and classifying authorship using this representation. To evaluate SAR, we compile 2 different sketch datasets collected from  a number of experienced artists. These datasets are designed to expose SAR to different levels of challenges and sketch variations so as to test its effectiveness in authorship recognition. These datasets, along with SAR source code, will be made publicly available to allow for further research in this field. \B{is this the contribution paragraph? usually contributions are made explicit}

%We hope that people in the community will find our databsets useful to use and research upon. Our collaborating artists who demonstrated through their work a great sketching abilities, have come from diverse artistic and sketching backgrounds as some of them are graphical designers and others are interior designer with an average sketching experience of 7 years and a maximum of 10 years.




%conducted to compare human versus computational sketch authorship recognition performance will be provided. After that, the development pipeline of SAR and the different techniques adopted will be provided. Towards the end of this paper, we share a number experimental results across different datasets that validate the use of SAR in authorship recognition.We will also present experimental results regarding different algorithmic variations we adopted and tested so that the community can use our findings and take them into consideration when conducting a research in the same field. Finally, we will demonstrate an application which is a training program that allows artists, designers and animators to test their affinity to any given artist, whose works have been incorporated into the machine learning part of the program.

